Comparing software variability across and within fMRI analysis packages

### 2022-02-21 paper/paper.tex
Update resutls with selecting max of WT samples

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistic.
Mean of differences in t-statistic maps is centered around zero for BT and WT
in both thresholded and unthresholded maps (t-test p~\textless~$10^{-5}$).
However, for each tool pair (A, B), BT variability was
significantly larger than WT in tool A or B,
with an order of magnitude larger standard deviation of differences 
in both thresholded and unthresholded maps, 
(Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$).
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, results show that BT and WT were not correlated across voxels
(Pearson's r $\approx 0$, p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps-corr}).
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.845                           & 2.639                              & -0.052                             & 1.122    & -0.059 & 0.911    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.871                           & 3.216                              & 0.048                             & 1.405    & -0.027 & 1.097    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.426                           & 3.214                              & -0.113                             & 1.543    & -0.104 & 1.208    \\
    {Within Tool}     & FSL          & -0.009                           & 0.266                              & 0.012                             & 0.046    & 0.004 & 0.042    \\
    {(WT)}            & SPM          & 0.000                           & 0.199                              & 0.000                             & 0.035    & 0.000 & 0.029    \\
    {}                & AFNI         & -0.004                           & 0.273                              & 0.000                             & 0.084    & 0.000 & 0.075    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in t-statistic maps.}
  \label{table:pipeline-stats}
\end{table}

@@

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistic maps (mean over subjects).
As for group-level maps, BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-4}$ for 14 subjects).
However, for some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj},
and see Supplemental Material~\ref{sec:supp-worst-subject}).
% As for the group maps, BT and WT
% showed no correlation across voxels for all subjects
% (r$\approx 0$, p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

%%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.9\textwidth]{figures/plots/Bland-Altman/with-masking/unthresh-sbj04.png}
  \caption{For subject with highest WT variability,
    unthresholded subject-level variability computed between tools (\textbf{A}), and within tools at machine error (\textbf{B}).}
    % and difference between them (\textbf{C}). \camille{If the changes are visible, I think that it would be useful to add the correspondant unthresholded maps for the reader to see where the differences are and what they "look like"}}
  \label{fig:unthresh-maps-sbj}
\end{figure*}

@@

While the previous results were obtained over the union of t-statistic maps between the pair of tools,
we also computed results in the intersection of maps and found that the brain masking instability was
triggered by both BT and WT.
BT and WT variabilities were consistently smaller than ones with the fixed masks
in both thresholded and unthresholded maps (see Table~\ref{table:pipeline-stats-fixed-mask}).
The effect of masking was clearly appeared in BT by Bland-Altman plots showing that blob lines
were removed after fixing masks (Figure~\ref{fig:unthresh-maps-mask}-\textbf{A},\textbf{B}).

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.668                           & 1.056                              & -0.033                             & 1.121    & -0.068 & 0.937    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.823                           & 1.857                              & 0.048                             & 1.439    & 0.034 & 1.146    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.645                           & 1.428                              & 0.064                             & 1.489    & -0.065 & 1.206    \\
    {Within Tool}     & FSL          & -0.025                           & 0.197                              & 0.012                             & 0.043    & 0.004 & 0.041    \\
    {(WT)}            & SPM          & -0.002                           & 0.154                              & 0.000                             & 0.033    & 0.000 & 0.028    \\
    {}                & AFNI         & -0.008                           & 0.208                              & 0.000                             & 0.078    & 0.000 & 0.072    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in intersected t-statistic maps.}
  \label{table:pipeline-stats-fixed-mask}
\end{table}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/4-marked.pdf}
  % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/5-framed.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{For subject with highest WT variability, unthresholded subject-level t-statistic
  within tools at machine error for FSL (\textbf{A}),
  SPM (\textbf{B}), AFNI (\textbf{C}).}% \camille{If I understand correctly the point you are making here is that WT(AFNI) at some voxels is close to AFNI-SPM ? What is surprising here for me is that WT(AFNI) seems to be quite different from WT(SPM) and WT(FSL). Do we have a good idea why? Maybe looking at the maps would help?}
  %\ali{We are pointing regions with instability in both WT and BT, and yes indeed it shows a very different WT(AFNI) compare to WT(FSL) and WT(SPM), but we did not investigate the reason of variabilities for now.} }
  \label{fig:unthresh-worst-sbj}
\end{figure*}

>>>>

Table~\ref{table:pipeline-stats} presents summary statistics for variability in the
group-level t-statistic.
Mean of differences in t-statistic maps was centered around zero for BT and WT
in both thresholded and unthresholded maps (t-test p~\textless~$10^{-5}$).
However, for each tool pair (A, B), BT variability was
significantly larger than WT in tool A or B,
with an order of magnitude larger standard deviation of differences 
in both thresholded and unthresholded maps, 
(Wilcoxon signed-rank test and t-test p~\textless~$10^{-5}$).
These global differences were confirmed by Bland-Altman plots showing a
clear dominance of BT over WT
(Figure~\ref{fig:unthresh-maps}-\textbf{A},\textbf{B}).
In addition, results show that BT and WT were not correlated across voxels
(Pearson's r $\approx 0$, p$< 10^{-5}$, Figure~\ref{fig:unthresh-maps-corr}).
% Interestingly, the correlation appears driven by a set of voxels exhibiting comparable BT and
% WT values located around the identity line in Figure~\ref{fig:unthresh-maps}D, which, however, did not seem to have
% any spatial consistency.

\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.845                           & 2.639                              & -0.052                             & 1.122    & -0.059 & 0.911    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.871                           & 3.216                              & 0.048                             & 1.405    & 0.027 & 1.097    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.426                           & 3.214                              & -0.113                             & 1.543    & -0.104 & 1.208    \\
    {Within Tool}     & FSL          & -0.397                           & 1.218                              & -0.020                             & 0.189    & 0.017 & 0.207    \\
    {(WT)}            & SPM          & 0.142                           & 1.035                              & 0.000                             & 0.139    & 0.000 & 0.126    \\
    {}                & AFNI         & -0.045                           & 1.282                              & 0.000                             & 0.373    & 0.000 & 0.355    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in t-statistic maps.}
  \label{table:pipeline-stats}
\end{table}

@@

Table~\ref{table:pipeline-stats} also presents summary statistics for
subject-level unthresholded t-statistic maps (mean over subjects).
As for group-level maps, the mean of differences in t-statistic maps was
approximately zero centered in both BT and WT (t-test p~\textless~$10^{-4}$ for 13 subjects),
and BT was consistently larger than WT (Wilcoxon
signed-rank test and t-test p~\textless~$10^{-4}$ for 14 subjects).
However, for some subjects and for AFNI, WT approached 
BT in some regions (Figure~\ref{fig:unthresh-maps-sbj},
and see Supplemental Material~\ref{sec:supp-worst-subject}).
% As for the group maps, BT and WT
% showed no correlation across voxels for all subjects
% (r$\approx 0$, p$< 10^{-5}$ for all subjects, see Supplemental Material~\ref{sec:supp-subjects} and~\ref{sec:supp-worst-subject}).

%%%%%%%%%% Var. of Unthresh sbj05%%%%%%%%
\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.9\textwidth]{figures/plots/Bland-Altman/with-masking/unthresh-sbj05.png}
  \caption{For subject with highest WT variability,
    unthresholded subject-level variability computed between tools (\textbf{A}), and within tools at machine error (\textbf{B}).}
    % and difference between them (\textbf{C}). \camille{If the changes are visible, I think that it would be useful to add the correspondant unthresholded maps for the reader to see where the differences are and what they "look like"}}
  \label{fig:unthresh-maps-sbj}
\end{figure*}

@@

While the previous results were obtained over the union of t-statistic maps between the pair of tools,
we also computed results in the intersection of maps and found that the brain masking instability was
triggered by both BT and WT.
BT and WT variabilities were consistently smaller than ones with the fixed masks
in both thresholded and unthresholded maps (see Table~\ref{table:pipeline-stats-fixed-mask}).
The effect of masking appeared in Bland-Altman plots by showing that blob lines
were removed after fixing masks (Figure~\ref{fig:unthresh-maps-mask}-\textbf{A},\textbf{B}).

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
  \centering
  \begin{tabular}{cccccc|cc}
    \toprule
                      &              & \multicolumn{4}{c|}{Group map}  & \multicolumn{2}{c}{Subject maps}                                                                     \\
    \multirow{2}{*}{} & {}           & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c|}{Unthresholded} & \multicolumn{2}{c}{Unthresholded}                               \\
    % \cmidrule{3-8}
    {}                & {}           & $\mu$                           & $\sigma$                           & $\mu$                             & $\sigma$ & $\mu$ & $\sigma$ \\
    \midrule
    \rowcolor{lightgray!50}
    {Between Tools}   & FSL vs. SPM  & -0.668                           & 1.056                              & -0.033                             & 1.121    & -0.068 & 0.937    \\
    \rowcolor{lightgray!50}
    {(BT)}            & FSL vs. AFNI & -0.823                           & 1.857                              & 0.048                             & 1.439    & 0.034 & 1.146    \\
    \rowcolor{lightgray!50}
    {}                & AFNI vs. SPM & 0.645                           & 1.428                              & 0.064                             & 1.489    & -0.065 & 1.206    \\
    {Within Tool}     & FSL          & 0.012                           & 0.127                              & 0.000                             & 0.165    & 0.017 & 0.199    \\
    {(WT)}            & SPM          & 0.002                           & 0.154                              & 0.000                             & 0.121    & 0.000 & 0.110    \\
    {}                & AFNI         & -0.003                           & 0.3548                              & 0.003                             & 0.285    & 0.000 & 0.328    \\
    \bottomrule
  \end{tabular}
  \caption{Voxel-wise mean and standard deviation of BT and WT variability in intersected t-statistic maps.}
  \label{table:pipeline-stats-fixed-mask}
\end{table}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{figures/5-marked.pdf}
  % \includegraphics[width=\textwidth]{figures/plots/wt-tstats/5-framed.png}
  % \includegraphics[width=.6\textwidth]{figures/sbj-abs-corr-unthresh-plot.png}
  \caption{For subject with highest WT variability, unthresholded subject-level t-statistic
  within tools at machine error for FSL (\textbf{A}),
  SPM (\textbf{B}), AFNI (\textbf{C}).}% \camille{If I understand correctly the point you are making here is that WT(AFNI) at some voxels is close to AFNI-SPM ? What is surprising here for me is that WT(AFNI) seems to be quite different from WT(SPM) and WT(FSL). Do we have a good idea why? Maybe looking at the maps would help?}
  %\ali{We are pointing regions with instability in both WT and BT, and yes indeed it shows a very different WT(AFNI) compare to WT(FSL) and WT(SPM), but we did not investigate the reason of variabilities for now.} }
  \label{fig:unthresh-worst-sbj}
\end{figure*}
